---
title: "PM566 assignment5"
author: "Mingzhi Ye"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
---

<br>

This is my PM566 assignment5 website. I will showcase a few interactive visuals here.

<br>

```{r setup, message=FALSE, echo=FALSE, warning=FALSE}

library(data.table)
library(tidyverse)
library(dplyr)
library(plotly)
library(DT)
library(knitr)
library(listviewer)
# Initialize code chunk options
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  eval=TRUE,
  echo = TRUE,
  cache = FALSE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618,
  out.width = "700px",
  class.source = "code-r")
```

```{css, echo = FALSE}
.code-r { /* Code block */
  font-size: 15px;
}

.code-r-small { /* Code block */
  font-size: 10px;
}
```

<br>



First I will source any necessary code, e.g. `process_covid_data.R`:

```{r load-data}
source("pollutiondata.R")
```

<br>

## Second step

Then I will add some code to create the **plotly** figures

#Average concentration of SO2 in 2018 and previous years

```{r plot1, class.source="code-r-small"}
data_s1 <- data_s %>%
  group_by(Date,year) %>%
  summarise(monitor_concentration:=mean(monitor_concentration,na.rm=TRUE))
data_s1<-as.data.frame(data_s1)
data_s1 %>% plot_ly(x = ~Date, y = ~monitor_concentration, color=~year, type = "scatter", mode = "lines",
        hoverinfo = 'text',
        text = ~paste(paste("Date: ", Date, sep=""),
                      paste("Concentration of SO2: ", monitor_concentration, sep=""),
                      paste("Year: ", year, sep=""), sep = "<br>")) %>%
  layout(title = "Average concentration of SO2 in 2018 and previous years",
                  yaxis = list(title = "Average concentration of SO2"), xaxis = list(title = "Date"),
         hovermode = "compare")

```

#Average concentration of CO in 2018 and previous years

```{r plot2, class.source="code-r-small"}
data_c1 <- data_c %>%
  group_by(Date,year) %>%
  summarise(monitor_concentration:=mean(monitor_concentration,na.rm=TRUE))
data_c1<-as.data.frame(data_c1)
data_c1 %>% plot_ly(x = ~Date, y = ~monitor_concentration, color=~year, type = "scatter", mode = "lines",
        hoverinfo = 'text',
        text = ~paste(paste("Date: ", Date, sep=""),
                      paste("Concentration of CO: ", monitor_concentration, sep=""),
                      paste("Year: ", year, sep=""), sep = "<br>")) %>%
  layout(title = "Average concentration of CO in 2018 and previous years",
                  yaxis = list(title = "Average concentration of CO2"), xaxis = list(title = "Date"),
         hovermode = "compare")

```

#Times of change in concentration of SO2 between 2018 and previous years

```{r plot3, class.source="code-r-small"}
data_s1<-data_s %>%
  group_by(county,year) %>%
  summarise(monitor_concentration=mean(monitor_concentration,na.rm=TRUE),
            latitude=mean(latitude,na.rm=TRUE),
            longitude=mean(longitude,na.rm=TRUE))
data_s1<-data.table(data_s1)
data_s2<-data_s1[year=="Previous years"]
data_s3<-data_s1[year=="2018"]
data_sx<-merge(x=data_s2,y=data_s3,
           by.x="county", by.y="county",
           all.x=TRUE,all.y=TRUE)
data_sx[,times:=monitor_concentration.y/monitor_concentration.x]
data_sx<-data_sx[,.(county,latitude.x,longitude.x,times)]

shadeLimit <- 2

fig <- data_sx %>%
  plot_ly(
    lat = ~latitude.x,
    lon = ~longitude.x,
    mode   = 'markers',
    marker = list(mode   = 'markers',
                  color = ~times,
                  colors = 'Purples',
                  size=~times*30
                  ),
    colors = 'Purples',
    type = 'scattermapbox',
    hoverinfo = 'text',
    text = ~paste( paste(county, ":", sep=""), paste(" The concentration of SO2 in 2018 is ", round(times,2)," times of that in previous years", sep=""),sep="<br>")
    )

fig <- fig %>%
  layout(
    title = "Times of change in concentration of SO2 between 2018 and previous years",
    mapbox = list(
      style = 'open-street-map',
      zoom =5,
      center = list(lon = -120, lat = 37)))

fig

```

#Times of change in concentration of CO between 2018 and previous years

```{r plot4, class.source="code-r-small"}
data_c1<-data_c %>%
  group_by(county,year) %>%
  summarise(monitor_concentration=mean(monitor_concentration,na.rm=TRUE),
            latitude=mean(latitude,na.rm=TRUE),
            longitude=mean(longitude,na.rm=TRUE))
data_c1<-data.table(data_c1)
data_c2<-data_c1[year=="Previous years"]
data_c3<-data_c1[year=="2018"]
data_cx<-merge(x=data_c2,y=data_c3,
           by.x="county", by.y="county",
           all.x=TRUE,all.y=TRUE)
data_cx[,times:=monitor_concentration.y/monitor_concentration.x]
data_cx<-data_cx[,.(county,latitude.x,longitude.x,times)]

shadeLimit <- 2

fig <- data_cx %>%
  plot_ly(
    lat = ~latitude.x,
    lon = ~longitude.x,
    mode   = 'markers',
    marker = list(mode   = 'markers',
                  color = ~times,
                  colors = 'Purples',
                  size=~times*30
                  ),
    colors = 'Purples',
    type = 'scattermapbox',
    hoverinfo = 'text',
    text = ~paste( paste(county, ":", sep=""), paste(" The concentration of CO in 2018 is ", round(times,2)," times of that in previous years", sep=""),sep="<br>")
    )

fig <- fig %>%
  layout(
    title = "Times of change in concentration of CO between 2018 and previous years",
    mapbox = list(
      style = 'open-street-map',
      zoom =5,
      center = list(lon = -120, lat = 37)))

fig

```
